Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-06 Thesis/chapter/031-theory-calculations.tex
MARS included to EMMA theory

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{EMMA}
%\Gls{emma} and \gls{mars}
\Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
Each time step the dependent variables for all possible input variable combinations
are predicted with the help of \gls{mars}. 
\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
"Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
The \texttt{CRAN} package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
%%% MARS 
\gls{mars} is an extension of multivariate linear regression.
Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g. kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensions (n>5). 
%to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
The main advancements are the ability to fit (possible complex) interactions and non-linearities. 
%- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
%% MARS MODEL SELECTION
%- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
The \gls{rf} is developed in a forward/backward stepwise recursive manner. 
During the forward recursion basis functions are added in pairs until a certain number of terms is reached. 
Then, the backwards algorithm regularizes the function by removing terms. 
The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}.

- "Choosing a previous term for multiplication (10) is analogous to choosing a (previous) region to split in (7). The optimization over 2, and t in (10) is quite similar to finding the optimal splitting variable and split point for partitioning a region. "\cite{friedman1988fitting}

\begin{equation}
    GCV(M) = \frac{1}{N} \sum_{i=1}^{N} \frac{ \left(y_i - \hat{f}(x_i) \right)^2 } {\left( 1- \frac{C(M)}{N}\right)^2 }
\end{equation}
with $M$ being the number of terms, $N$ the number of data points, $d$ the degrees of freedom and
\begin{equation}
    C(M) = (d + 1)M + 1
\end{equation}

%%Advantages of \gls{mars} are its easy interpretability and flexibility to model non-linearity and of course ability to cope with high dimensional data\cite{villanova2010function}.

- the interpretability of $\hat{f}(x)$ is important to understand $f(x)$ spaces of increasing dimension."\cite{friedman1988fitting}
%
- the error is due to unmeasured and uncontrolled

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{EMMA}
%\Gls{emma} and \gls{mars}
\Gls{emma} is an implementation of the \gls{pso} in the \texttt{R} programming language. 
Each time step the dependent variables for all possible input variable combinations %$\mathbf{x} = \{x_1,\cdots ,x_N\}$ 
are predicted with the help of \gls{mars}. 
The \gls{mars} \gls{rf} is then used to chose the next position for each particle.
\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
"Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
The \texttt{CRAN} package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
%%% MARS 
\gls{mars} is an extension of multivariate linear regression.
Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g. kernel functions), whose number of parameter quickly exceeds the practical for moderate dimensions ($n>5$). 
%
%to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
%"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
%
The main advancements are the ability to fit (possible complex) interactions and non-linearities. 
%
%- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
%% MARS MODEL SELECTION
%- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
%
%%% FORWARD MARS
The \gls{rf} is developed in a forward/backward stepwise recursive manner. 
During the forward recursion basis functions are added in pairs until a certain number of terms is reached. 
Each pair consists of two hinge functions (also called rectifier functions) multiplied with a term already part of the \gls{rf} including the constant term.
The maximum degree of interaction is 2 for \gls{emma}, but can be varied. 
This means that only two basis functions can be multiplied (excluding the constant term) to form a subsequent term.
Pairwise added hinge functions are of the simple form $h(x-c)$ and $h(c-x)$ where $h(a)= max(0,a)$ and with $x$ being an independent variable, $c$ being a constant and $a$ being any expression. 
%%% BACKWARD EMMA
Then, the backwards algorithm regularizes the function by removing individual terms. 
The metric which decides if a term should be removed is called \gls{gcv} and was introduced by Wahba and Cravenin 1969\cite{wahba1979smoothing}.

\begin{equation}
    GCV(M) = \frac{1}{N} \sum_{i=1}^{N} \frac{ \left(y_i - \hat{f}(x_i) \right)^2 } {\left( 1- \frac{C(M)}{N}\right)^2 }
\end{equation}
with $M$ being the number of terms, $N$ the number of data points, a correction term
\begin{equation}
    C(M) = (d + 1)M + 1
\end{equation}
and penalty is $d=3$ for interactions larger than 1 and $d=2$ otherwise.
The variable of the hinge functions and its knot location at the forward step and which terms to delete 
at the backwards step are selected by minimizing \gls{gcv}. 
The coefficients for each term are then chosen via regular \gls{mse} minimisation\cite{friedman1988fitting}.

%%Advantages of \gls{mars} are its easy interpretability and flexibility to model non-linearity and of course ability to cope with high dimensional data\cite{villanova2010function}. 
%- the interpretability of $\hat{f}(x)$ is important to understand $f(x)$ spaces of increasing dimension."\cite{friedman1988fitting}

### 2022-11-06 Thesis/chapter/061-results-emma.tex
MARS included to EMMA theory

%%% EQUATION 
%\subsubsection{Equation}
Equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} and \ref{eq:emma-phd4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
and $h(6-\lambda)$ into layer count influential only if under 6.
%
The first thing to notice is that prediction functions of each generation depend on the same variables. 
%This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
This stems from the fact that the algorithm must chose a single minimal set of \gls{bf} to predict all dependent variables. 
%
%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
%As the \gls{mars} algorithm is greedy,
%Different independent variables compete to be used as \gls{bf} in the prediction functions because of the greediness of the \gls{mars} algorithm. 
%}

@@

%%% PROBLEMS 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error from variance due to dependency. 
This is mainly because of the curse of dimensionality \td{cite} which makes it hard to collect enough data for each dimension. 
The main problem about too many independent variables is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
This effect is reinforced by the choice of two independent variables as dependent variables (IVDV). 
Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
for including them in the \gls{rf} is a easy way to reduce the \gls{mse}.
These \gls{bf}s then "take places" \td{(cf. musical chairs)} of \gls{bf}s predicting other dependent variables in the \gls{rf}. 
This in turn can lead to wrong predictions and therefore inefficient choice of future samples.

>>>>

%%% EQUATION 
%\subsubsection{Equation}
Equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} and \ref{eq:emma-phd4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
%$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
and $h(6-\lambda)$ into layer count influential only if under 6.
%
The first thing to notice is that prediction functions of each generation depend on the same variables. 
%This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
This stems from the fact that the algorithm must chose a single minimal set of \gls{bf} to predict all dependent variables. 
%
%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
%As the \gls{mars} algorithm is greedy,
%Different independent variables compete to be used as \gls{bf} in the prediction functions because of the greediness of the \gls{mars} algorithm. 
%}

@@

%%% PROBLEMS 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error (due to unmeasured and uncontrolled variables) from variance due to dependency of chosen dependent varibales. 
This is mainly because of the curse of dimensionality \td{cite} which makes it hard to collect enough data for each dimension. 
The main problem about too many independent variables is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
This effect is reinforced by the choice of two independent variables as dependent variables (IVDV). 
Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
for including them in the \gls{rf} is a easy way to reduce the \gls{mse}.
These \gls{bf}s then "take places" \td{(cf. musical chairs)} of \gls{bf}s predicting other dependent variables in the \gls{rf}. 
This in turn can lead to wrong predictions and therefore inefficient choice of future samples.
